ChemKED: a human- and machine-readable data standard for chemical kinetics experiments

### 2017-10-02 rebuttal.tex

    Finally, each released version of PyKED is permanently archived on Zenodo
    (\url{https://doi.org/10.5281/zenodo.597935}) so that it is accessible should a user wish to use
    an old version to solve a compatibility issue temporarily.
    %
\end{response}

\begin{reviewer}
    %
    18.~Page 7, line 12, \texttt{mole-percent}, \texttt{mole-fraction}, and \texttt{mass-fraction}
    include a dash in their name, whereas this is not the case for the example on page 5 line 48 and
    in the description of the composition element on page 4, line 47.

    19.~Same issue as \#18 holds for page 7, line 17.
    %
\end{reviewer}

\begin{response}
    %
    This was a typo in the manuscript. All of the keywords here include spaces in their name, both
    in the YAML schema and in the PyKED interface. This has been corrected in the manuscript and we
    have added a test to the PyKED package to ensure the values are correct.
    %
\end{response}

@@

\begin{reviewer}
    %
    20.~I think it would be more clear if \texttt{volume\_history}, \texttt{compression\_time},
    \texttt{compressed\_temperature}, and \texttt{compressed\_pressure} would be combined.

    The line: `if the ChemKED file encodes an RCM experiment' is unnecessarily repeated.
    %
\end{reviewer}

\begin{response}
    %
    We have consolidated the RCM-specific information into a separate list, and eliminated the
    duplicated phrase.
    %
\end{response}

### 2017-10-02 pyked.tex
Respond to #36
Consolidate the RCM-specific attributes into one list.

The \pybox|DataPoint| class stores the information associated with a single data
point in the \ck{} file (i.e., a single element of the \yabox|datapoints|
sequence). Similar to the \pybox|ChemKED| class,
the \pybox|DataPoint| stores information as instance attributes:
%
\begin{itemize}
    \item \pybox|equivalence_ratio|: The value of the equivalence ratio, if
    present. For informational purposes only---no validation is done of the
    value.
    \item \pybox|ignition_delay|, \pybox|temperature|, \pybox|pressure|,
    \pybox|pressure_rise|: The value of these data are stored as instances of
    the \pybox|Quantity| class from the Pint \autocite{Grecco2016} package,
    possibly with associated uncertainty
    \item \pybox|composition|: A list of dictionaries of the species and their
    respective amounts. The values are validated so that \yabox|mole percent|,
    \yabox|mole fraction|, or \yabox|mass fraction| cannot be mixed for a single
    data point, and so that the sum of the values is approximately 1.0, or
    100.0 for \yabox|mole percent|.
    \item \pybox|composition_type|: A string indicating the type of composition
    information for the data point---one of \pybox|'mole percent'|,
    \pybox|'mole fraction'|, or \pybox|'mass fraction'|
    \item \pybox|volume_history|: If the \yabox|volume-history| of an RCM
    experiment is provided in the \ck{} file, it is stored in this attribute as
    a \pybox|namedtuple|, and the actual values are stored in NumPy arrays
    \autocite{vanderWalt:2011np}
    \item \pybox|compression_time|: If the \ck{} file encodes an RCM experiment,
    the length of the compression stroke may be included
    \item \pybox|compressed_temperature|: If the \ck{} file encodes an RCM experiment,
    the temperature at the end of compression may be included
    \item \pybox|compressed_pressure|: If the \ck{} file encodes an RCM experiment,
    the pressure at the end of compression may be included
    \item \pybox|ignition_type|: A dictionary specifying the method of the
    measurement of ignition delay
\end{itemize}

@@

Only the first author is printed when \pybox|Reference| or
\pybox|Reference:Authors| is selected because the whole author list may be
quite long.

>>>>

The \pybox|DataPoint| class stores the information associated with a single data
point in the \ck{} file (i.e., a single element of the \yabox|datapoints|
sequence). Similar to the \pybox|ChemKED| class,
the \pybox|DataPoint| stores information as instance attributes:
%
\begin{itemize}
    \item \pybox|equivalence_ratio|: The value of the equivalence ratio, if
    present. For informational purposes only---no validation is done of the
    value.
    \item \pybox|ignition_delay|, \pybox|temperature|, \pybox|pressure|,
    \pybox|pressure_rise|: The value of these data are stored as instances of
    the \pybox|Quantity| class from the Pint \autocite{Grecco2016} package,
    possibly with associated uncertainty
    \item \pybox|composition|: A list of dictionaries of the species and their
    respective amounts. The values are validated so that \yabox|mole percent|,
    \yabox|mole fraction|, or \yabox|mass fraction| cannot be mixed for a single
    data point, and so that the sum of the values is approximately 1.0, or
    100.0 for \yabox|mole percent|.
    \item \pybox|composition_type|: A string indicating the type of composition
    information for the data point---one of \pybox|'mole percent'|,
    \pybox|'mole fraction'|, or \pybox|'mass fraction'|
    \item \pybox|ignition_type|: A dictionary specifying the method of the
    measurement of ignition delay
\end{itemize}

If the \ck{} file encodes an RCM experiment, there are several specialized fields that can be
included.

\begin{itemize}
    \item \pybox|volume_history|: If the \yabox|volume-history| of an RCM
    experiment is provided in the \ck{} file, it is stored in this attribute as
    a \pybox|namedtuple|, and the actual values are stored in NumPy arrays
    \autocite{vanderWalt:2011np}
    \item \pybox|compression_time|: The duration of the compression stroke
    \item \pybox|compressed_temperature|: The estimated reactor temperature at the end of the
    compression stroke
    \item \pybox|compressed_pressure|: The measured reactor pressure at the end of the compression
    stroke
\end{itemize}

@@

Only the first author is included in the \pybox|DataFrame| when \pybox|Reference| or
\pybox|Reference:Authors| is selected because the whole author list may be
quite long.
